---
title: Getting started with QuikQuan
author: An introductory tutorial with examples
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with QuikQuan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package provides tools for fitting kernel quantile regression.

The strengths and improvements that this package offers relative to other quantile regression packages are as follows:

* Compiled Fortran code significantly speeds up the kernel quantile regression estimation process.

* Solve non-crossing kernel quantile regression.

For this getting-started vignette, first, we will use a real data set named as `GAGurine`
in the package `MASS`, which collects the concentration of chemical GAGs in the urine of 314 children aged 0 to 17 years.
We used the concentration of GAG as the response variable.

```{r}
library(QuikQuan)
library(MASS)
data(GAGurine)
x <- as.matrix(GAGurine$Age)
y <- GAGurine$GAG
```

## `fastkqr()`
Given an input matrix `x`, a quantile level `tau`, and a response vector `y`,
a kernel quantile regression model is estimated for a sequence of penalty
parameter values. The other main arguments the users might supply are:

* `lambda`: a user-supplied `lambda` sequence.
* `tau`: a user-supplied `tau` value for a quantile level.
* `is_exact`: exact or approximated solutions.

```{r}
lambda <- 10^(seq(1, -4, length.out=10))
fit <- fastkqr(x, y, lambda=lambda, tau=0.1, is_exact=TRUE)
```

## `cv.fastkqr()`

This function performs k-fold cross-validation (cv). It takes the same
arguments as `fastkqr`.

```{r}
cv.fit <- cv.fastkqr(x, y, lambda=lambda, tau=0.1)
```

## Methods

A number of S3 methods are provided for `fastkqr` object.

* `coef()` and `predict()` return a matrix of coefficients and predictions $\hat{y}$ given a matrix `X` at each lambda respectively. The optional `s` argument may provide a specific value of $\lambda$ (not necessarily
part of the original sequence).


```{r}
coef <- coef(fit, s = c(0.02, 0.03))
predict(fit, x, tail(x), s = fit$lambda[2:3])
```

## `fastnckqr()`
Given an input matrix `x`, a sequence of quantile levels `tau`, and a response vector `y`,
a non-crossing kernel quantile regression model is estimated for two sequences of penalty
parameter values. It takes the same arguments `x`, `y`,`is_exact`, which are specified above.
The other main arguments the users might supply are:

* `tau`: a user-supplied `tau` sequence for quantile levels.

* `lambda2`: a user-supplied `lambda1` sequence for the L2 penalty.

* `lambda1`: a user-supplied `lambda2` sequence for the smooth ReLU penalty.

```{r}
l2 <- 1e-4
tau <- c(0.1, 0.3, 0.5, 0.7, 0.9)
l1_list <- 10^seq(-8, 2, length.out=10)
fit1 <- fastnckqr(x ,y, lambda1 = l1_list, lambda2 = l2,  tau = tau)
```

## `cv.fastnckqr()`

This function performs k-fold cross-validation (cv). It takes the same
arguments as `fastnckqr`.

```{r}
l2_list <- c(1e-3, 1e-4)
cv.fit1 <- cv.fastnckqr(x, y, lambda1=l1_list, lambda2=l2, tau=tau)
```

## Methods

A number of S3 methods are provided for `fastnckqr` object.

* `coef()` and `predict()` return an array of coefficients and predictions $\hat{y}$ given a matrix `X` and `lambda2` at each lambda1 respectively. The optional `s1` argument may provide a specific value of $\lambda_1$ (not necessarily
part of the original sequence).

* `cross.fastnckqr()` and `objective.fastnckqr` return a vector of crossing numbers and objective values given a matrix `X` and `lambda2` at each lambda1 respectively. 


```{r}
cross <- cross.fastnckqr(fit1, x, s2=l2, s1=l1_list)
obj <- objective.fastnckqr(fit1, x, y, s2=l2)
coef <- coef(fit1, s2=1e-4, s1 = l1_list[2:3])
predict(fit1, x, tail(x), s1=l1_list[1:3], s2=l2)
```
